Assessing primitives performance\\ on multi-stage execution

### 2018-05-18 paper.tex
update asm comp figures, nr of loc, some typos

\begin{table*} [bth]
\centering
\begin{tabular}{c|cccc|ccc}
   &  \multicolumn{4}{c|}{Software maintenance \& evolution} & \multicolumn{3}{c}{Primitive execution time}\\
  \hline
    & Recompilation & Familiar to & Lines & Number of & Stack switch & Optimization & Code generation \\
    & required & developers & of code & implementations & overhead & potential & control \\
  \hline
  \legBase    & No & All  & 10  & 0 & No & - & - \\
   \hline
  \legSlangPlug & Plugin & VM & 35  & 1  & Yes & Limited & Low \\
   \hline
  \legSlang   & Yes  & VM & 45  & 1  & Yes & High & Low \\
   \hline
  \legRTL   & Yes  & VM-JIT & 85  & 2  & No & High & High \\
  \hline
\end{tabular}
\caption{Comparison between implementations.\vspace{-0.5cm}}
\label{tab:cmp_implem}
\end{table*}

@@

\paragraph{Control over generated code.} One can notice a rather striking performance difference between the 2 set-ups we have.In \GCCLinux, the performance between the \legSlang and \legRTL implementations is really close for long strings (1000 characters wide), with respectively 25.24 and 26.76 relative speed-up factors for a 1000-characters string. Yet performance greatly differs when the \LLVMMac set-up is used, with respectively 12,94 and 24,88 relative speed-up factors.

>>>>

\begin{table*} [bth]
\centering
\begin{tabular}{c|cccc|ccc}
   &  \multicolumn{4}{c|}{Software maintenance \& evolution} & \multicolumn{3}{c}{Primitive execution time}\\
  \hline
    & Recompilation & Familiar to & Lines & Number of & Stack switch & Optimization & Code generation \\
    & required & developers & of code & implementations & overhead & potential & control \\
  \hline
  \legBase    & No & All  & 10  & 0 & No & - & - \\
   \hline
  \legSlangPlug & Plugin & VM & 35  & 1  & Yes & Limited & Low \\
   \hline
  \legSlang   & Yes  & VM & 35  & 1  & Yes & High & Low \\
   \hline
  \legRTL   & Yes  & VM-JIT & 85  & 2  & No & High & High \\
  \hline
\end{tabular}
\caption{Comparison between implementations.\vspace{-0.5cm}}
\label{tab:cmp_implem}
\end{table*}

@@

\paragraph{Control over generated code.} One can notice a rather striking performance difference between the 2 set-ups we have. In \GCCLinux, the performance between the \legSlang and \legRTL implementations is really close for long strings (1000 characters wide), with respectively 25.24 and 26.76 relative speed-up factors for a 1000-characters string. Yet performance greatly differs when the \LLVMMac set-up is used, with respectively 12,94 and 24,88 relative speed-up factors.
